README.md

### 2021-05-16 README.Rmd
journal issue 🌅

> Fernández-Pascual E & Correia-Álvarez E (2021) [Mire microclimate: Groundwater buffers temperature in waterlogged versus dry soils.](https://doi.org/10.1002/joc.6893) *International Journal of Climatology*.

>>>>

> Fernández-Pascual E & Correia-Álvarez E (2021) [Mire microclimate: Groundwater buffers temperature in waterlogged versus dry soils.](https://doi.org/10.1002/joc.6893) *International Journal of Climatology* 41, E2949-E2958.
